My Findings

### 2024-07-22 Findings (Shared Folder)/Chapters/modelAttempts.tex
new notes to the lab report
new updates

>>>>

\subsection{Optimal Transport}
I just came across this \href{https://www.math.ucdavis.edu/~qlxia/summary/transport.html}{website} about the computational approaches to the optimal transport. I was shocked how similar their plots was to the vascular structures.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\linewidth]{images/optimalTransportAndAngiogenesis}
	\label{fig:optimaltransportandangiogenesis}
\end{figure}
\FloatBarrier
After this observation and looking at some similar plots it just came to me that the angiogenesis is really an optimal transport problem where we want to deliver nutrients and oxygen in an efficient way to every single cell of the body. The work by \cite{Pegon2019-ww} triggered this idea to see if I can use some of the theoretical tools developed in the optimal transport literature to my benefit.
